### 2018-03-20 paper/sexSelectionSpacing-ver1.tex
Fix figure reference
Discuss changes in sex ratios results

The results so far show that as sex ratios became more
male-biased the spacing when a woman has only girls became 
longer relative to other sex compositions, presumably because
of increased use of sex selection rather than a reduction in son preference.
Neither the median spacing or the conditional survival curves
can, however, provide us with information on how the use of
sex selection vary \emph{within} a spell.
Furthermore, using conditional survival curves forces everybody 
to finish the spell in the same month and does not provide
any information about how many births there are.
We can, however, learn something about both changes in 
sex selection within a spell and the likelihood of exiting
with a birth using standard  survival curves.

The predicted sex ratio may change within a spell for, at
least, two reasons.
First, parents may stop using prenatal sex determination 
once the duration from the previous birth becomes long enough
because they prefer not to have their children too far apart.
In this case we should observe the predicted sex ratio decline
with spell length.
Second, if the degree of son preference vary within the sample
but behavior is not affected by duration from the previous birth,
we should observe an increasing share of births come from 
parents with stronger son preference as duration from the
previous birth increases.
Whereas the early births are a combination of births to
people with lower son preference and those with stronger son
preference who conceived a son in the first or second pregnancy,
later births are then predominately from those with stronger
son preference who have not yet conceived a son.
Hence, in this case we should see an increase in the sex ratio 
as duration increases.

% Examples of declining sex ratios

@@

% Examples of increasing sex ratios

\begin{figure}[htpb!]
\centering
\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
\setcounter{subfigure}{-2}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
\setcounter{subfigure}{0}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\caption{Predicted probability of having a boy and probability of 
no birth yet from nine months after second birth for urban women with
eight or more years of education 
for the 1995--2004 and 2005--2016 periods
} 
\label{fig:decreasing_sex_ratio} 
\end{figure}

\section{Discussion}

[conditional survival curves]
72 months = 6 years, plus the 9 months from the previous birth.

[TK not sure where this fits in]
In addition, it is possible that falling fertility also generically 
leads to longer spacing between births.
This means that we have to separate out which part of the longer
spacing comes from falling fertility (and therefore should also
affect boy composition) and which parts comes from increased use
of sex selection.

[We should expect sex selection to be mainly used for the last---or close to
last---birth that a couple expect to have because of the cost and risk
of the procedures.]

@@

\appendix
\section{Online Appendix}

>>>>

The results so far show that as sex ratios became more
male-biased the spacing when a woman has only girls became 
longer relative to other sex compositions, presumably because
of increased use of sex selection rather than a reduction in son preference.
Neither the median spacing or the conditional survival curves
can, however, provide us with information on how the use of
sex selection vary \emph{within} a spell.
Furthermore, using conditional survival curves forces everybody 
to finish the spell in the same month and does not provide
any information about how many births there are.
We can, however, learn something about both changes in 
sex selection within a spell and the likelihood of exiting
with a birth using standard  survival curves.
The predicted sex ratio may change within a spell for, at
least, two reasons.

@@

\begin{figure}[htpb!]
\centering
\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
\setcounter{subfigure}{-2}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
\setcounter{subfigure}{0}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\caption{Predicted probability of having a boy and probability of 
no birth yet from nine months after second birth for urban women with
eight or more years of education 
for the 1995--2004 and 2005--2016 periods
} 
\label{fig:increasing_sex_ratio} 
\end{figure}

First, parents may stop using prenatal sex determination 
once the duration from the previous birth becomes long enough
because they prefer not to have their children too far apart.
In this case we should observe the predicted sex ratio decline
with spell length.

Second, if the degree of son preference across women within the sample
but behavior is not affected by duration from the previous birth,
we should observe an increasing share of births come from 
parents with stronger son preference as duration from the
previous birth increases.
Whereas the early births are a combination of births to
people with lower son preference and those with stronger son
preference who conceived a son in the first or second pregnancy,
later births are then predominately from those with stronger
son preference who have not yet conceived a son.
Hence, in this case we should see an increase in the sex ratio 
as duration increases.

Figures \ref{fig:decreasing_sex_ratio} and \ref{fig:increasing_sex_ratio} show
examples of how sex ratio behave within spells.
Both are for women with eight or more education since the results above indicate
that they are the most likely to use sex selection or other means of achieving 
an unequal sex ratio.
Figure \ref{fig:decreasing_sex_ratio} shows results for the second spell for
the 1995--2004 and 2005--2016 periods for women with a girl as their first
child by area of residence.
Figure \ref{fig:increasing_sex_ratio} shows results for the third spell for
the same two periods for urban women with either two girls or one boy and one
girl as their first two children.%
\footnote{
There is no evidence of unequal sex ratios in either period for similar women 
with two boys as their first two children as shown in Figure TK.
}

Within the second spell, both urban and rural women show a declining
sex ratio as duration increases for the 1995--2004 period, whereas there
is little change, or possibly a small increase, with duration for the 
2005-2016 period.
These results are consistent with a situation where fertility is declining
over time leaving less room for a change in the decision to use sex selection.
Fertility decline is not immediately obvious from the second spell 
results, but the third spell show that the likelihood of progressing from
two to third children declines by approximately 15 percentage points if
the woman has given birth to a boy, and, as the Appendix shows, only about 
25\% of urban women with two boys have a third child in the 2005--2016 period, 
down from close to 40\% in the 1995--2004 period. 
Furthermore, it is unlikely that a substantial number of births will take
place after the end of the spell period, which is equal to six year in
addition to the nine months from the previous birth to the start of the spell.

The third spell figures show a very different situation with almost no 
change in sex ratios with duration for women with two girls, but substantial 
increases in sex ratios with duration for women with one boy and one girl.
The high, but stable, sex ratio for women with two girls is likely 
motivated by the combined desire to limit fertility and ensure a son;
similarly to the situation for the second spell as shown in 
Figure \ref{fig:decreasing_sex_ratio} (b) and (d).

The increase in sex ratio with duration for women who already have
given birth to a boy likely illustrates the case where there are a
combination of degrees of son preference.
Say that one group wants one son and after that will not use sex
selection, whereas another group has a strong preference for two
sons (or either have or expect to lose the boy they already have)
and that the two groups conceive at the same rate.
In that case, we should expect exactly the increasing sex ratios
we observe, especially given the declining fertility over time.

@@

\appendix
\section{Descriptive Statistics}
